Autonomous Oceanographic Data Collection towards Estimating Excursion Sets of Vector-valued Random Fields

### 2020-06-17 eibv.tex
Updates from Overleaf

>>>>

\textcolor{red}{C.T.: This doesn't work, we cannot be that short on the definition of EIBV, it is highly unclear. I suggest we go for the following notation:
$$\operatorname{IBV}(\bm{x}; \bm{y})
$$ denotes the IBV under the current law of the field, conditioned on observing $\bm{y}$ at $\bm{x}$ (generalized, possibly batch observation). Then
$$
\operatorname{EIBV}(\bm{x}):=\mathbb{E}_{\bm{Y}}\left[\textrb{IBV}(\bm{x}; \bm{Y})\right]
$$
where $\bm{Y}$ is distributed according to the current law of $Z_{\bm{x}}$.}

\textcolor{red}{
The philosophy is the following: EIBV and EEMV are functionals of a probability distribution. Then, if not mentioned explicitly, the probability distribution will be taken to be the current law of the field. (This notation is highly efficient).}

\textcolor{red}{When one want to consider several steps, one can use $\textrm{IBV}_{n}(\bm{x}; \bm{y})$ to denote the fact that the starting point (starting probability distribution) is the law of the field at the $n$-th step $\mathbb{P}_n$ to which conditioning on $\bm{y}$ at $\bm{x}$ is added.}

\textcolor{red}{For a rigorous definition
$$
\operatorname{IBV}(\bm{x}; \bm{y}):=\int_{\domain}
\mathbb{P}\left(\gp[\uu]\in T\mid Z_{\bm{x}}=\bm{y}\right)(1-\mathbb{P}\left(\gp[\uu]\in T \mid Z_{\bm{x}}=\bm{y}\right))
d\mes(u) \\
$$
where $\mathbb{P}$ denotes the current law of the field.}
